Continuous developmental change explains discontinuities in word learning

### 2019-09-08 journal/ms_blind.tex
journal submission

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Continuous developmental change explains discontinuities in word learning},
            pdfauthor={Abdellah Fourtassi, Sophie Regan, \& Michael C. Frank},
            pdfkeywords={word learning, cognitive development, computational modeling},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{lineno}

\linenumbers
\usepackage{tipa}
\usepackage[sortcites=false,sorting=none]{biblatex}

\authornote{ Abdellah Fourtassi

Department of Psychology

Stanford University

50 Serra Mall

Jordan Hall, Building 420

Stanford, CA 94301

@@

Cognitive development is sometimes characterized in terms of a
succession of discontinuous stages (Piaget, 1954). Although intuitively
appealing, this sort of stage theories can be challenging to integrate
with theories of learning, which typically posit that knowledge and
skills improve incrementally with experience. Indeed, one of the central
challenges of cognitive development has been to explain transitions
between stages which appear to be qualitatively different (Carey, 2009).

Nevertheless, at least in some cases, development may only appear to be
stage-like. Some discontinuities may be related to how we measure a
specific skill. Other discontinuities may emerge due to statistical
thresholding (e.g., p-value \textless{} 0.05) which can create a
spurious dichotomy between success and failure in observing a given
behavior. In such cases, positing discontinuous stages is unnecessary.
Instead, a continuous model --- involving similar representations across
the lifespan --- may provide a simpler and more transparent account of
development (see also McMurray (2007) and Shultz, Schmidt, Buckingham,
and Mareschal (1995)).

We use a case study from word learning literature. Stager and Werker
(1997) first showed that children's early ability to distinguish similar
sounds does not automatically translate into word learning skills. The
authors measured word learning using an audio-visual habituation Switch
task. First, infants are familiarized with two word-object pairings
(e.g., label 1 with object 1 and label 2 with object 2). Second, they
are tested using two types of trials. The control \enquote{same} trial
consists of a correct pairing (e.g., label 1 with object 1) and the
\enquote{switch} trial consists of a wrong pairing (e.g., label 1 with
object 2). If babies have correctly learned the association during the
familiarization, they are supposed to be surprised by the
\enquote{switch} trial and not by the \enquote{same} trial. The former
should thus result in a greater looking time compared to the latter
(Werker, Cohen, Lloyd, Casasola, \& Stager, 1998).

@@

The initial discontinuous interpretation has been challenged by
subsequent work. For instance, Yoshida, Fennell, Swingley, and Werker
(2009) investigated whether failure in the Switch task reflects a lack
of sound encoding during \emph{familiarization}, or whether it is only
due to the nature of the \emph{testing} method which does not allow
learning below a certain threshold to be detected. They used the same
familiarization procedure as Stager and Werker (1997), but instead of
comparing the looking times in \enquote{same} and \enquote{switch}
trials, they tested infants using a two-alternative choice task
comparing fixations to target and distractor objects (Fernald, Perfors,
\& Marchman, 2006; Golinkoff, Hirsh-Pasek, Cauley, \& Gordon, 1987).
Using this testing method, the researcher found evidence for learning
even in 14-month olds.

@@

Some researchers (Pajak et al., 2016; Swingley, 2007; Yoshida et al.,
2009) proposed that word knowledge may not be encoded in a binary
fashion, i.e., it is not the case that children either succeed or fail
in encoding minimal contrast when learning the meanings. Rather, they
may be encoding this knowledge in a graded fashion (see also Munakata
(2001)). According to this view, development does not so much involve a
qualitative shift (i.e., a sudden emergence of an ability that did not
exist before) as much as it consists in the continuous refinement of
initially noisy knowledge.

@@

In the Switch task (Stager \& Werker, 1997), children are understood to
succeed if they reject a wrong association (e.g., \enquote{bih} with
object 2). However, a large overlap between \enquote{bin} and
\enquote{din} means that \enquote{bih} is itself a plausible
mispronunciation of \enquote{dih}. The wrong association may not be
rejected by children because the speaker could have said \enquote{bih}
but meant \enquote{dih}. In the two-alternative choice task (Yoshida et
al., 2009), children do not have to reject the wrong association; they
only need to show a preference for the correct one. Given a label, e.g.,
\enquote{bih}, they pick which object is a better match to this label.
Though it is possible that the speaker said \enquote{bih} and meant
\enquote{dih}, it is \emph{more} likely that the speaker both said and
meant \enquote{bih} --- this higher probability leads to a preference
for the correct object.

@@

Finally, development can be understood as an increase in the precision
(i.e., a decrease in the variance) of the probabilistic knowledge,
leading to a lower overlap between the distributions of similar-sounding
words (Figure \ref{fig:illus}, right). Importantly, a more precise
representation still has a non-zero variance --- Learning difficulties
can still be induced with challenging stimuli or in cognitively
demanding situations as was demonstrated in adults studies (Pajak et
al., 2016; White et al., 2013).

\subsection{This study}\label{this-study}

@@

The present work proposes a model of word-pair learning based on the
probabilistic account. We tested the ability of this model to both
\emph{explain} various findings in previous experiments in both children
and adults (e.g., the fact that similar words are harder to learn than
different words) and to \emph{predict} new learning patterns that have
not been tested before (i.e., the effect of the referents' similarity on
word learning). We explore the extent to which the probabilistic account
allows us to understand development in terms of as a continuous
refinement in similar representations across the lifespan.

The paper is organized as follows. First, we introduce the model and we
explain how it allows us to characterize behavior in a
word-pair-learning paradigm. Then we explore the predictions of the
model through simulating its behavior across different parameter
settings. Next, we quantify the extent to which the model's predictions
account for human data we collected from both preschool children and
adults. Finally, we discuss the results in the lights of existing
accounts of word development.

@@

@@

\begin{figure}[htbp]
\centering
\includegraphics{ms_files/figure-latex/simulation-1.pdf}
\caption{\label{fig:simulation}The predicted probability of accurate
responses in the testing phase as a function of stimuli distinctiveness
\(\Delta s\) and \(\Delta o\) and representation precision \(\sigma\)
(For simplicity, we use model 2, which assumes that
\(\sigma\)=\(\sigma_C\)=\(\sigma_L\)). Dashed line represents chance.}
\end{figure}

@@

In this experiment, we tested participants in the word learning task
introduced above (Figure \ref{fig:task}). More precisely, we explored
the predictions related to both distinctiveness and precision. Sound
similarity (\(\Delta s\)) and object similarity (\(\Delta o\)) were
varied simultaneously in a within-subject design. Two age groups
(preschool children and adults) were tested on the same task to explore
whether development can be characterized with the uncertainty
parameters, \(\sigma_C\) and \(\sigma_L\). The experiment, sample size,
exclusion criteria and the model's main predictions were
pre-registered.\footnote{https://osf.io/942gv/}

@@

We report data from \(N=\) 63 children ages 4-5 years from the Bing
Nursery School on Stanford University's campus. An additional \(N=\) 39
children participated but were removed from analyses (using
preregistered exclusion criteria) because they were not above chance on
the catch trials due to the challenging nature of our procedure (see
below). We also report data from \(N=\) 74 adult participants tested on
Amazon Mechanical Turk. An additional \(N=\) 26 were tested but removed
from analyses (again, using preregistered exclusion criteria) because
they had low scores on the catch trials or because they were familiar
with the non-English sound stimuli we used in the adult experiment.

@@

{\centering \includegraphics{ms_files/figure-latex/stim-1}

@@

In the exposure trials, participants saw two objects associated with
their corresponding sounds. We presented the first object on the left
side of the tablet's screen simultaneously with the corresponding sound.
The second sound-object association followed on the other side of the
screen after 500ms. For both objects, visual stimuli were present for
the duration of the sound clip (about 800ms). In the testing trials,
participants saw both objects simultaneously and heard only one sound.
They completed the trial by selecting which of the two objects
corresponded to the sound. The object-sound pairings were randomized
across participants, as was the order of the conditions (except for the
catch condition which was always placed in the middle of the testing
sequence). We also randomized the on-screen position (left vs.~right) of
the two pictures on each testing
trial.\footnote{The experiment can be viewed online at https://tinyurl.com/word-pair-learning-experiment}

@@

{\centering \includegraphics{ms_files/figure-latex/allData-1}

@@

For object distance, we found \(\beta =\) 0.60 (\(p\) \textless{}
0.001), and this finding confirms the new prediction of our model,
according to which, object distance also modulates success in word
learning. Note, in particular, that increasing the visual similarity of
the objects makes children succeed in learning the similar-sounding
words. Finally, for the age group, we obtained \(\beta =\) 0.59 (\(p\)
\textless{} 0.001), showing that overall performance improves with age.
The full output of the regression model is shown in the Appendix.

@@

\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/kidswitch}}}
\vspace{1em}

\section{Appendix}\label{appendix}

We show in Table 2 the output of the regression model we used to analyze
behavioral data in the experiment.

@@

\section{Acknowledgements}\label{acknowledgements}

This work was supported by a post-doctoral grant from the Fyssen
Foundation, NSF \#1528526, and NSF \#1659585.

\section{Disclosure statement}\label{disclosure-statement}

@@

@@

@@

>>>>

\documentclass[english,,man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Continuous developmental change explains discontinuities in word learning},
            pdfauthor={Abdellah Fourtassi, Sophie Regan, \& Michael C. Frank},
            pdfkeywords={word learning, cognitive development, computational modeling},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\usepackage{tipa}
\usepackage[sortcites=false,sorting=none]{biblatex}

\authornote{

@@

Cognitive development is often characterized in terms of a succession of
discontinuous stages. In Piaget's initial conception, these stages
cross-cut different aspects of cognition (Piaget, 1954); in more modern
conceptions, distinct domains are often thought to progress on their own
timeline (e.g., Carey, Zaitchik, \& Bascandziev, 2015). Although
intuitively appealing, this sort of stage theory can be challenging to
integrate with theories of learning, which typically posit that
knowledge and skills improve incrementally with experience. Indeed, one
of the central challenges of cognitive development has been to explain
transitions between stages which appear to be qualitatively different
(Carey, 2009).

Nevertheless, at least in some cases, development may only appear to be
stage-like. Some discontinuities may be related to how we measure a
specific skill. Other discontinuities may emerge due to statistical
thresholding (e.g., an experimental p-value of \(p < .05\) for one age
group but not another) which can create a spurious dichotomy between
success and failure in observing a given behavior. In such cases,
positing discontinuous stages is unnecessary. Instead, a continuous
model --- involving similar representations across the lifespan --- may
provide a simpler and more transparent account of development (cf.
McMurray, 2007; Shultz, Schmidt, Buckingham, \& Mareschal, 1995).

To explore this point computationally, we use a case study from word
learning literature. Stager and Werker (1997) first showed that
children's early ability to distinguish similar sounds does not
automatically translate into word learning skills. The authors measured
word learning using an audio-visual habituation Switch task. First,
infants are familiarized with two word-object pairings (e.g., label 1
with object 1 and label 2 with object 2). Second, they are tested using
two types of trials. The control \enquote{same} trial consists of a
correct pairing (e.g., label 1 with object 1) and the \enquote{switch}
trial consists of a wrong pairing (e.g., label 1 with object 2). If
babies have correctly learned the association during the habituation,
they are supposed to be surprised by the \enquote{switch} trial and not
by the \enquote{same} trial. The former should thus result in a greater
looking time compared to the latter (Werker, Cohen, Lloyd, Casasola, \&
Stager, 1998).

@@

The initial discontinuous interpretation has been challenged by
subsequent work. For instance, Yoshida, Fennell, Swingley, and Werker
(2009) investigated whether failure in the Switch task reflects a lack
of sound encoding during \emph{habituation}, or whether it is only due
to the nature of the \emph{testing} method which does not allow learning
below a certain threshold to be detected. They used the same habituation
procedure as Stager and Werker (1997), but instead of comparing the
looking times in \enquote{same} and \enquote{switch} trials, they tested
infants using a two-alternative choice task comparing fixations to
target and distractor objects (Fernald, Perfors, \& Marchman, 2006;
Golinkoff, Hirsh-Pasek, Cauley, \& Gordon, 1987). Using this testing
method, researchers found evidence for learning even in 14-month olds.

@@

Some researchers (Pajak et al., 2016; Swingley, 2007; Yoshida et al.,
2009) proposed that word knowledge may not be encoded in a binary
fashion, i.e., it is not the case that children either succeed or fail
in encoding minimal contrast when learning the meanings. Rather, they
may be encoding this knowledge in a graded fashion (see Munakata (2001)
for an detailed discussion of a similar view). Thus, development does
not so much involve a qualitative shift (i.e., a sudden emergence of an
ability that did not exist before) as much as it consists in the
continuous refinement of initially noisy knowledge.

@@

In the Switch task (Stager \& Werker, 1997), children are understood to
succeed if they reject a wrong association (e.g., \enquote{bih} with
object 2). However, a large overlap between \enquote{bih} and
\enquote{dih} means that \enquote{bih} is itself a plausible
mispronunciation of \enquote{dih}. The wrong association may not be
rejected by children because the speaker could have said \enquote{bih}
but meant \enquote{dih}. In the two-alternative choice task (Yoshida et
al., 2009), children do not have to reject the wrong association; they
only need to show a preference, albeit small, for the correct one. Thus,
unlike the Switch, this testing method allows us to see subtle evidence
of learning even with a large overlap. For example, given the label
\enquote{bih}, children are supposed to pick which object is a better
match to this label. Though it is possible that the speaker said
\enquote{bih} and meant \enquote{dih}, it is \emph{more} likely that the
speaker both said and meant \enquote{bih} --- this higher probability
leads to a preference for the correct object.

@@

In this framework, developmental change can be understood as an increase
in the precision (i.e., a decrease in the variance) of the probabilistic
knowledge, leading to a lower overlap between the distributions of
similar-sounding words (Figure \ref{fig:illus}, right). Importantly, a
more precise representation still has a non-zero variance. Thus,
learning difficulties can still be induced with challenging stimuli or
in cognitively demanding situations as was demonstrated in adults
studies (Pajak et al., 2016; White et al., 2013).

\subsection{The current study}\label{the-current-study}

@@

The present work proposes a model of word-pair learning based on the
probabilistic account. We tested the ability of this model to both
\emph{explain} various findings in previous experiments in both children
and adults (e.g., the fact that similar words are harder to learn than
different words) and to \emph{predict} new learning patterns that have
not been tested before. In particular, we test the prediction that
referent similarity (i.e., the confusability of pictures referred to by
novel words) should play an identical computational role to word form
similarity in predicting recognition difficulty. Although this
prediction is intuitive, to our knowledge, it has never been tested.
Finally, we explore the extent to which the probabilistic account allows
us to understand development in terms of as a continuous refinement in
similar representations across the lifespan.

The paper is organized as follows. First, we introduce the model and we
explain how it allows us to characterize behavior in a
word-pair-learning paradigm. Then we explore the predictions of the
model through simulating its behavior across different parameter
settings. Next, we quantify the extent to which the model's predictions
account for human data we collected from both preschool children and
adults. Finally, we discuss the results in the light of existing
accounts of word development.

@@

where \(\Delta s = s_2-s_1\).

@@

\begin{figure}[htbp]
\centering
\includegraphics{ms_blind_files/figure-latex/simulation-1.pdf}
\caption{\label{fig:simulation}The predicted probability of accurate
responses in the testing phase as a function of stimuli distinctiveness
\(\Delta s\) and \(\Delta o\) and representation precision \(\sigma\)
(For simplicity, we use model 2, which assumes that
\(\sigma\)=\(\sigma_C\)=\(\sigma_L\)). Dashed line represents chance.}
\end{figure}

@@

In this experiment, we tested participants in the word learning task
introduced above (Figure \ref{fig:task}). More precisely, we explored
the predictions related to both distinctiveness and precision. Sound
similarity (\(\Delta s\)) and object similarity (\(\Delta o\)) were
varied simultaneously in a within-subject design. Two age groups
(preschool children and adults) were tested on the same task\footnote{This
  four-condition within-subject design is relatively novel for
  preschoolers, but we followed the tablet paradigm (e.g., Frank,
  Sugarman, Horowitz, Lewis, \& Yurovsky, 2016) which allowed us to
  gather a relatively large number of trials from each child.} to
explore whether development can be characterized with the uncertainty
parameters, \(\sigma_C\) and \(\sigma_L\). The experiment, sample size,
exclusion criteria, and the model's main predictions were
pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}

@@

We report data from \(N=\) 63 children ages 4-5 years from a nursery
school. An additional \(N=\) 39 children participated but were removed
from analyses (using preregistered exclusion criteria) because they were
not above chance on the catch trials due to the challenging nature of
our procedure (see below). We also report data from \(N=\) 74 adult
participants tested on Amazon Mechanical Turk. An additional \(N=\) 26
were tested but removed from analyses (again, using preregistered
exclusion criteria) because they had low scores on the catch trials or
because they were familiar with the non-English sound stimuli we used in
the adult experiment.

@@

{\centering \includegraphics{ms_blind_files/figure-latex/stim-1}

@@

In the exposure trials, participants saw two objects associated with
their corresponding sounds. We presented the first object on the left
side of the tablet's screen simultaneously with the corresponding sound.
The second sound-object association followed on the other side of the
screen after 500ms. For both objects, visual stimuli were present for
the duration of the sound clip (about 800ms). In the testing trials,
participants saw both objects simultaneously and heard only one sound.
They completed the trial by selecting which of the two objects
corresponded to the sound. The object-sound pairings were randomized
across participants, as was the order of the conditions (except for the
catch condition which was always placed in the middle of the testing
sequence). We also randomized the on-screen position (left vs.~right) of
the two pictures on each testing trial.

@@

{\centering \includegraphics{ms_blind_files/figure-latex/allData-1}

@@

For object distance, we found \(\beta =\) 0.60 (\(p\) \textless{}
0.001), and this finding confirms the new prediction of our model,
according to which, object distance also modulates success in word
learning. Note, in particular, that increasing the visual similarity of
the objects makes children succeed in learning the similar-sounding
words. Finally, for the age group, we obtained \(\beta =\) 0.59 (\(p\)
\textless{} 0.001), showing that overall performance improves with age.
The full output of the regression model is shown in Table 2.

@@

\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at [Due to the doube-blind review, the link to the github repository is only provided in the full version addressed to the editor]}}
\vspace{1em}

@@

@@

\hypertarget{ref-carey2015}{}
Carey, S., Zaitchik, D., \& Bascandziev, I. (2015). Theories of
development: In dialog with jean piaget. \emph{Developmental Review},
\emph{38}.

@@

\hypertarget{ref-frank2016}{}
Frank, M. C., Sugarman, E., Horowitz, A. C., Lewis, M., \& Yurovsky, D.
(2016). Using tablets to collect data from young children. \emph{Journal
of Cognition and Development}, \emph{17}(1).

@@

\clearpage

\renewcommand{\listfigurename}{Figure captions}

\listoffigures
